\LARGE \bf Mixed Non-Bayesian and DeGroot Learning

### 2012-12-11 docs/paper.tex
Description of why random draw method fails

@@

In order to characterize the effect of naive DeGroot nodes on Non-Bayesian social learning we simulated time taken for convergence versus the ratio of Non-Bayesian to DeGroot nodes in a network.  This simulation was performed for a several graph types: Barabasi-Albert preferential attachment~\cite{Barabasi}, Kleinberg small-world~\cite{KleinbergSmallWorld}, Eppstein power law~\cite{Eppstein}, and the complete graph.  To simulate the spread of information throughout the network, only 50\% of the Non-Bayesian received any signals; the other 50\% needed to rely completely on learning from their neighbors.  Each trial was run 100 times for each ratio percentage between from 1-100\%, for a total of 10,000 trials for each graph type.

\begin{figure*}[t]
%\hspace*{0.1in}
%\centerline{\includegraphics[scale=0.8]{figures/nb_ratio}}
\centering
\includegraphics[width=0.9\textwidth]{figures/nb_ratio}
\caption{Time to convergence decreases as the ratio of Non-Bayesian to DeGroot nodes decreases}
\label{fig:nb_ratio}
\end{figure*}

>>>>

\subsection{Random Draw Belief Conversion Method}

An important discovery from simulation was that the random draw method of conversion from DeGroot to Non-Bayesian belief described in section~\ref{sec:draw_from_degroot} can lead to unrealistically skewed belief distributions.  This primarily occurred in cases using Gaussian distributions where the means of the possible distributions represented by each belief state $\theta_i \in \Theta$ are relatively far apart.  For example, suppose that $n = 2$, $\theta_0 \sim N(100, 1)$ and $\theta_1 \sim N(105, 1)$.  A DeGroot node $d$ will have an initial belief of 102.5, and will therefore create a Bayesian belief distribution by drawing from the distribution $N(102.5, 1)$.  There is now a significant (0.318) probability that it will draw a point at least one standard deviation outside of the mean, e.g. $s_{d,t}^\prime = 101.5$.  But the value 101.5 is significantly more likely to have been drawn from the probability distribution $N(100, 1)$ versus the distribution $N(105, 1)$.  Therefore $d$ will report that it is almost certain that the true state is $\theta_0 \sim N(100, 1)$ when in reality it should have a relatively evenly spread belief distribution.

After the discovery of this difficulty, we evaluated the distance metric described in section~\ref{sec:likelihood_metric} and found it to give much more desirable results.  Therefore that method was used throughout all simulations described in the remainder of this section.

@@

In order to characterize the effect of naive DeGroot nodes on Non-Bayesian social learning we simulated time taken for convergence versus the ratio of Non-Bayesian to DeGroot nodes in a network.  This simulation was performed for a several graph types: Barabasi-Albert preferential attachment~\cite{Barabasi}, Kleinberg small-world~\cite{KleinbergSmallWorld}, Eppstein power law~\cite{Eppstein}, and the complete graph.  To simulate the spread of information throughout the network, only 50\% of the Non-Bayesian nodes received any signals; the other 50\% needed to rely completely on learning from their neighbors.  Each trial was run 100 times for each ratio percentage between from 1-100\%, for a total of 10,000 trials for each graph type.

\begin{figure*}[h]
%\hspace*{0.1in}
%\centerline{\includegraphics[scale=0.8]{figures/nb_ratio}}
\centering
\includegraphics[width=0.9\textwidth]{figures/nb_ratio}
\caption{Time to convergence decreases as the ratio of Non-Bayesian to DeGroot nodes decreases}
\label{fig:nb_ratio}
\end{figure*}
